%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


%---------------------------------------------------------
\begin{cvparagraph}
    Publications are listed in reversed chronological order.
\end{cvparagraph}

\begin{cvpublications}
\begin{pubitems} 
% 9---------------------------------------
\item {Mengfei Sun, \textbf{\underline{Jie Wu}}, Jin Li*, Brendan Mccane, Nan Yang, Xianghe Ma, Borui Wang, Minghui Zhang. Conditional Autoencoder for Generating BNS Waveforms with Tidal and Precession Effects. \href{https://arxiv.org/abs/2503.19512}{arXiv:2503.19512.}}

% 8---------------------------------------
\item {\textbf{\underline{Jie Wu}}, Mengfei Sun, Xianghe Ma, Xiaolin Liu, Jin Li*, and Zhoujian Cao*. Effect of kick velocity on gravitational wave detection of binary black holes with space- and ground-based detectors. \href{https://arxiv.org/abs/2502.13710}{arXiv:2502.13710.}}

% 7---------------------------------------
\item {Xianghe Ma, Borui Wang, Nan Yang, Jin Li*, Brendan McCane, Mengfei Sun, \textbf{\underline{Jie Wu}}, Minghui Zhang, Yan Meng*. Identification of Stochastic Gravitational Wave Backgrounds from Cosmic String Using Machine Learning. \href{https://arxiv.org/abs/2502.11804}{arXiv:2502.11804.}}

% 6---------------------------------------
\item {Yalin Hu, \textbf{\underline{Jie Wu}}, Haiyan Luo, Guanqi Su, Xiangxi Meng, Liyu Liu, and Guo Chen*. Parallel manipulation of multiple ink droplets via near-infrared light on lubricant infused surface. \href{https://pubs.aip.org/aip/apl/article/126/2/021602/3330590}{\textit{Appl. Phys. Lett.} \textbf{126}, 021602 (2025)}.}

% 5---------------------------------------
\item {\textbf{\underline{Jie Wu}}, Mengfei Sun, and Jin Li*. Constraints and detection capabilities of GW polarizations with space-based detectors in different TDI combinations. \href{https://arxiv.org/abs/2411.03631}{arXiv:2411.03631.}}

% 4---------------------------------------
\item {\textbf{\underline{Jie Wu}} and Jin Li*. Prospects of constraining on the polarizations of gravitational waves from binary black holes using space-and ground-based detectors. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.110.084057}{\textit{Phys. Rev. D} \textbf{110}, 084057 (2024)}. \href{https://arxiv.org/abs/2407.13590}{arXiv:2407.13590.}}

% 3---------------------------------------
\item \textbf{\underline{Jie Wu}}, Jin Li*, Xiaolin Liu, and Zhoujian Cao. Comparison and application of different post-Newtonian models for inspiralling stellar-mass binary black holes with space-based GW detectors. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.109.104014}{\textit{Phys. Rev. D} \textbf{109}, 104014 (2024)}. \href{https://arxiv.org/abs/2401.03113}{arXiv:2401.03113.}

% 2---------------------------------------
\item \textbf{\underline{Jie Wu}} and Jin Li*. Subtraction of the confusion foreground and parameter uncertainty of resolvable galactic binaries on the networks of space-based gravitational-wave detectors. \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.108.124047}{\textit{Phys. Rev. D} \textbf{108}, 124047 (2023)}. \href{https://arxiv.org/abs/2307.05568}{arXiv:2307.05568.}

% 1---------------------------------------
\item \textbf{\underline{Jie Wu}}, Jin Li*, and Qing-Quan Jiang*. Application of Newtonian approximate model to LIGO gravitational wave data processing (Suggested by editors). \href{https://cpb.iphy.ac.cn/EN/10.1088/1674-1056/acd8a3}{\textit{Chin. Phys. B} \textbf{32}, 090401 (2023)}.
\end{pubitems}
\end{cvpublications}